Synthesizing Symmetric Lenses

### 2018-07-07 papers/SymmetricLenses/main.tex
make disconnect change
make some changes

In contrast to the identity lens, the disconnect lens, \Disconnect, leaves data
unconnected. The disconnect lens takes four arguments: two regular expressions
and two strings. The regular expressions specify the formats of the
corresponding data on the two sides while the strings provide default values.
On creates, the input values are thrown away, and default values are returned ($\CreateROf{\String} =
\lstinline{"UNK"}$), and on puts, the second argument is used, and the first is
thrown away ($\PutROf{\String}{\StringAlt} = \StringAlt$).  In
our extended example, the \lstinline{salary} and
\lstinline{company} fields are independent, so we use the disconnect lens to relate them. The defaults are strings that indicate the information is missing.
%
\begin{lstlisting}
disconnect(salary, company, "unk", "UNK") : salary $\Leftrightarrow$ company
\end{lstlisting}
%
The insert \lstinline{ins} and delete \lstinline{del} lenses are
syntactic sugar for uses of the disconnect lens in which a string
constant is omitted entirely from the source and target formats,
respectively.
\begin{lstlisting}
 ins($t$) = disconnect("", $t$, "", $t$)
 del($s$) = disconnect($s$, "", $s$, "")
\end{lstlisting}

@@

\begin{center}
  \begin{tabular}{rcl}
    \Regex{},\RegexAlt{}
    & \GEq{} & $\String$ \\
    & \GBar{} & $\PRegexStar{\Regex}{p}$ \\
    & \GBar{} & $\RegexConcat{\Regex_1}{\Regex_2}$ \\
    & \GBar{} & $\PRegexOr{\Regex_1}{\Regex_2}{p}$
  \end{tabular}
\end{center}

@@

@@

\begin{center}
  \begin{tabular}{@{}r@{\hspace{1em}}c@{\hspace{1em}}l@{}r@{}}
    \RegexConcat{(\RegexConcat{\Regex{}}{\Regex'})}{\Regex''} & $\SSREquiv$ & \RegexConcat{\Regex{}}{(\RegexConcat{\Regex'}{\Regex''})} & \ConcatAssocRule{}  \\
    \PRegexOr{(\PRegexOr{\Regex}{\Regex'}{\Probability_1})}{\Regex''}{\Probability_2} & $\SSREquiv$ & \PRegexOr{\Regex}{(\PRegexOr{\Regex'}{\Regex''}{\frac{(1-\Probability_1)*\Probability_2}{1 - \Probability_1 * \Probability_2}})}{\Probability_1*\Probability_2} & \OrAssociativityRule{}  \\
    \PRegexOr{\Regex{}}{\RegexAlt{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\RegexAlt{}}{\Regex{}}{1-\Probability} & \OrCommutativityRule{}\\
    \RegexConcat{\Regex{}}{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}}{\Regex{}'})}{(\RegexConcat{\Regex{}}{\Regex{}''})}{\Probability} & \DistributivityLeftRule{} \\
    \RegexConcat{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})}{\Regex{}} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}'}{\Regex{}})}{(\RegexConcat{\Regex{}''}{\Regex{}})}{\Probability} & \DistributivityRightRule{} \\
    \RegexConcat{\EmptyString{}}{\Regex{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityLeftRule{} \\
    \RegexConcat{\Regex{}}{\EmptyString{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityRightRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\Regex{}}{\PRegexStar{\Regex{}}{\Probability}})}{1-\Probability} & \UnrollstarLeftRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\PRegexStar{{\Regex{}}}{\Probability}}{\Regex{}})}{1-\Probability} & \UnrollstarRightRule{} 
  \end{tabular}
\end{center}

@@

\subsection{Stochastic Regular Expression Entropy}
The entropy of a data source $S$ is $-\Sigma_{s\in S}P(s)\Log_2P(s)$, the
expected number of bits required to describe a random element in $S$. The
entropy of a stochastic regular expression can be computed directly from its
syntax, when the stochastic regular expression is unambiguous.
\begin{center}
  \begin{tabular}{rcl}
    $\EntropyOf{s}$
    & =
    & 1\\

@@

\begin{theorem}
  \label{thm:correct_entropy}
  If $\Regex$ is unambiguous and contains no empty subcomponents,
  $\EntropyOf{\Regex}$ is the entropy of $\Regex$.
\end{theorem}

>>>>

In contrast to the identity lens, the \Disconnect lens, leaves data
unconnected. The disconnect lens takes four arguments: two regular expressions
and two strings. The regular expressions specify the formats of the
corresponding data on the two sides while the strings provide default values.
On creates, the input values are thrown away, and default values are returned ($\CreateROf{\String} =
\lstinline{"UNK"}$), and on puts, the second argument is used, and the first is
thrown away ($\PutROf{\String}{\StringAlt} = \StringAlt$).  In
our extended example, the \lstinline{salary} and
\lstinline{company} fields are independent, so we use the disconnect lens to relate them. The defaults are strings that indicate the information is missing.
%
\begin{lstlisting}
disconnect(salary, company, "unk", "UNK") : salary $\Leftrightarrow$ company
\end{lstlisting}
%
The insert \lstinline{ins} and delete \lstinline{del} lenses are
syntactic sugar for uses of the disconnect lens in which a string
constant is omitted entirely from the source and target formats,
respectively.
\begin{lstlisting}
 ins($t$) = disconnect("", $t$, "", $t$)
 del($s$) = disconnect($s$, "", $s$, "")
\end{lstlisting}

@@

\begin{center}
  \begin{tabular}{rcl}
    \Regex{},\RegexAlt{}
    & \GEq{} & $\String$ \\
    & \GBar{} & $\emptyset$ \\
    & \GBar{} & $\PRegexStar{\Regex}{p}$ \\
    & \GBar{} & $\RegexConcat{\Regex_1}{\Regex_2}$ \\
    & \GBar{} & $\PRegexOr{\Regex_1}{\Regex_2}{p}$
  \end{tabular}
\end{center}

@@

    $\ProbabilityOf{\emptyset}{\String}$
    & =
    & $0$ \\

@@

\begin{center}
  \begin{tabular}{@{}r@{\hspace{1em}}c@{\hspace{1em}}l@{}r@{}}
    \PRegexOr{\Regex}{\emptyset}{1} & $\SSREquiv$ & \Regex{} & \OrIdentityRule{} \\
    $\RegexConcat{\Regex}{\emptyset}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionRightRule{} \\
    $\RegexConcat{\emptyset}{\Regex}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionLeftRule{} \\
    \RegexConcat{(\RegexConcat{\Regex{}}{\Regex'})}{\Regex''} & $\SSREquiv$ & \RegexConcat{\Regex{}}{(\RegexConcat{\Regex'}{\Regex''})} & \ConcatAssocRule{}  \\
    \PRegexOr{(\PRegexOr{\Regex}{\Regex'}{\Probability_1})}{\Regex''}{\Probability_2} & $\SSREquiv$ & \PRegexOr{\Regex}{(\PRegexOr{\Regex'}{\Regex''}{\frac{(1-\Probability_1)*\Probability_2}{1 - \Probability_1 * \Probability_2}})}{\Probability_1*\Probability_2} & \OrAssociativityRule{}  \\
    \PRegexOr{\Regex{}}{\RegexAlt{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\RegexAlt{}}{\Regex{}}{1-\Probability} & \OrCommutativityRule{}\\
    \RegexConcat{\Regex{}}{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}}{\Regex{}'})}{(\RegexConcat{\Regex{}}{\Regex{}''})}{\Probability} & \DistributivityLeftRule{} \\
    \RegexConcat{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})}{\Regex{}} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}'}{\Regex{}})}{(\RegexConcat{\Regex{}''}{\Regex{}})}{\Probability} & \DistributivityRightRule{} \\
    \RegexConcat{\EmptyString{}}{\Regex{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityLeftRule{} \\
    \RegexConcat{\Regex{}}{\EmptyString{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityRightRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\Regex{}}{\PRegexStar{\Regex{}}{\Probability}})}{1-\Probability} & \UnrollstarLeftRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\PRegexStar{{\Regex{}}}{\Probability}}{\Regex{}})}{1-\Probability} & \UnrollstarRightRule{} 
  \end{tabular}
\end{center}

@@

\subsection{Stochastic Regular Expression Entropy}
The entropy of a data source $S$ is the expected number of bits required to
describe a random element in $S$ ($-\Sigma_{s\in S}P(s)\Log_2P(s)$). The entropy
of a stochastic regular expression can be computed directly from its syntax,
when the stochastic regular expression is unambiguous, and contains no nonempty
components.
\begin{center}
  \begin{tabular}{rcl}
    $\EntropyOf{s}$
    & =
    & 1\\

@@

\begin{theorem}
  \label{thm:correct_entropy}
  If $\Regex$ is unambiguous and does not contain $\emptyset$ as a subterm,
  $\EntropyOf{\Regex}$ is the entropy of $\Regex$.
\end{theorem}

Without unambiguity constraints it is not easy to calculate the entropy. For
example, consider the SRE $\PRegexOr{\lstinline{"a"}}{\lstinline{"a"}}{.5}$.
Using the above computation, this SRE has an entropy of $1$, but the entropy
should be $0$. Similar issues occur when trying to find the entropy when
$\emptyset$ is a subterm, so we do not define the entropy on $\emptyset$.

In our work, we do not find this to be a problem, we require unambiguous regular
expressions as input to our synthesis procedure, and we can easily preprocess
emptysets out of the stochastic regular expressions that are themselves nonempty
by traversing the correct star-semiring equivalences
(\PRegexOr{\emptyset}{\lstinline{"s"}}{.5} \SSREquiv \lstinline{"s"}).
